---
title: "Production validation report"
output: word_document
params:
  results: NA
---

```{r include = FALSE}
library(data.table)

USER <-
  regmatches(
    params$results$session_info$swsContext.username,
    regexpr(
      "(?<=/).+$",
      params$results$session_info$swsContext.username,
      perl = TRUE
    )
  )

tab <- params$results$crops$original_outliers
tab[, flag := paste(flagObservationStatus, flagMethod, sep = ",")]
tab[, c("flagObservationStatus", "flagMethod", "Protected") := NULL]
tab[measuredElement == "production", measuredElement := "5510"]
tab[measuredElement == "area", measuredElement := "5312"]
tab[measuredElement == "yield", measuredElement := "5421"]
tab[, ratio := round(ratio, 2)]
tab[, MeanOld := round(MeanOld, 0)]
tab[, Value := round(Value, 1)]

setnames(
  tab,
  c("geographicAreaM49", "measuredElement", "measuredItemCPC", "timePointYears"),
  c("M49", "element", "CPC", "year")
)
```

Report generated by user `r USER` on `r Sys.Date()`. Contact:
`r params$results$session_info$swsContext.userEmail`

# Crops

The table below shows all the combinations of items/elements
that were found to have at least one outlier during the period
`r paste(sort(unique(params$results$crops$original_data$timePointYears)), collapse = ", ")`.
The column `status` indicates what action was taken:

* `pass`: the item was not an outlier (false positive)
* `action`: some action was undertaken (observations blanked or modified)

<br />

```{r, echo = FALSE}
# The `params` object is available in the document.
res <-
  merge(
    unique(params$results$crops$original_outliers[, c("geographicAreaM49", "measuredItemCPC"), with = FALSE]),
    params$results$crops$fixed_outliers,
    by = c("geographicAreaM49", "measuredItemCPC"),
    all.x = TRUE
  )

res$status[is.na(res$status)] <- ""

knitr::kable(res)
```

# Detailed tables

## Crops

All outliers

```{r, echo = FALSE}
  knitr::kable(tab)
```
